Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-15 chi2012.tex
done with interaction design section

\subsubsection{Coreference consolidation: Drag-and-Drop Same-As}

@@

Related to the concept of co-reference, PS.2 revealed that enumerated values of properties were often inconsistent, e.g. ``Casual dining'' vs ``Relaxed'' for a restaurant's ``atmosphere'' property. To reoncile such differences, so that they can be uniformly compared, we extended the drag and drop support of co-reference combination to support enumerated literal values as well,  This effectively allowed de-duplicated histograms and other visualisations to be made.

\subsubsection{Model-based brushing}

Since it can get confusing having an instance represented in multiple groups,

@@

\subsubsection{Adaptive visualisation modes}

\subsection{Summary of interaction features}

>>>>

\subsubsection{Coreference consolidation: Drag-and-Drop Same-as}

@@

Related to the concept of co-reference, PS.2 revealed that enumerated values of properties were often inconsistent, e.g. ``Casual dining'' vs ``Relaxed'' for a restaurant's ``atmosphere'' property. To reoncile such differences, so that items from corresponding datasources can be effectively compared, we extended the drag and drop support of co-reference combination to support enumerated literal values as well.

\subsubsection{``Do What I Mean'' Visualisation}

To make it easier for people to quickly visually compare aspects of instances, we created a charting tool and integrated a mapping feature.  To make these tools suitable for fast use, e.g. data exploration, we designed these tools to automatically configure display parameters instances or groups of were dropped on them, rather than making users manually specify them. In the current prototype, the DWIM behaviour of the chart automatically sets whether the plot is a histogram representation (counts of values) or numeric value display based upon the types of the dereferenced values being plotted; values that are non-numeric are counted, while numeric values are displayed.    Similarly, the map was made to detect address strings and latitude/longitude pairs, geocoding them where appropriate, and determining the optimal bounding box to display all items at maximum zoom.

\subsubsection{Model-based brushing}
Since it can get confusing having a single instance represented across several groups, we provided \emph{universal brushing} across the interface; hovering over any representation of any instance (an instance block, a map marker or a histogram bar), causes all other visible representations of that instance to lightly glow, so that the user can quickly identify all the places that a single instance is represented

@@

\subsection{Summary of interaction capabilities}

%% TODO
